%-------------------------
% Resume in Latex
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING----------
% \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
%   \textbf{\href{http://sourabhbajaj.com/}{\Large Sourabh Bajaj}} & Email : \href{mailto:sourabh@sourabhbajaj.com}{sourabh@sourabhbajaj.com}\\
%   \href{http://sourabhbajaj.com/}{http://www.sourabhbajaj.com} & Mobile : +1-123-456-7890 \\
% \end{tabular*}

\begin{center}
    \textbf{\Huge \scshape MK} \\ \vspace{1pt}
    \small 07... $|$ London,UK $|$ \href{mailto:x@xcom}{\underline{x@x.com}} $|$ 
    \href{https://linkedin.com/in/x}{\underline{linkedin.com/in/x}} $|$
    \href{https://github.com/x}{\underline{github.com/x}}
\end{center}

%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
 \resumeSubheading
      {Birkbeck, University of London}{}
      {Master of Science, Computer Science (Distance Learning)} {April 2026 -- 2028}
 \resumeSubheading
      {University of West London}{}
      {Bachelor of Science (Hons), Multimedia Computing with Music Technology} {}
 \resumeSubheading
      {Braze}{}
      {Braze Certification Email Deliverability Skills Badge} {}
  \resumeSubHeadingListEnd

%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Email Developer \& Front End Developer}{Aug 2011 -- Present}
      {Self-Employed Contractor}{London, UK}
      \resumeItemListStart
        \resumeItem{Built responsive sites and landing pages with clean, accessible markup.}
        \resumeItem{Developed HTML email templates compatible with major clients and ESPs.}
        \resumeItem{Debugged rendering issues across browsers and email clients.}
        \resumeItem{Integrated tracking, tagging, and basic data-layer requirements.}
        \resumeItem{Implemented iterative fixes based on analytics and stakeholder feedback.}
        \resumeItem{Delivered work in fast cycles for agencies and brands with shifting requirements.}
        \resumeItem{Worked with: UK Home Office, Dishoom, Jack Wills, La Senza, Lipsy London, Ann Summers, Ryman, Boux Avenue, Kickers, Speedo, Berghaus, Boxfresh, The White Company, Shelter, AKQA, Made Tech, Wunderman, Tribal Worldwide, Havas, TBG Digital, Isobar, The Mill, Tanget, FCB London, FutureBrand}
    \resumeItemListEnd

    \resumeSubheading
      {Email Marketing Specialist}{September 2025 -- November 2025}
      {4Motion}{London, UK}
      \resumeItemListStart
        \resumeItem{Reviewed sending patterns, list quality, and engagement data to maintain healthy performance.}
    \resumeItem{Tracked bounce types, complaint levels, and engagement shifts through Klaviyo reporting.}
    \resumeItem{Used segment and campaign analytics to identify weak audiences and adjust sending approach.}
    \resumeItem{Built hygiene workflows and suppression rules to keep lists clean and stable.}
    \resumeItem{Guided non-technical stakeholders through email deliverability best practices.}
      \resumeItemListEnd

    \resumeSubheading
      {English Teacher Volunteer}{Feb 2025 -- Aug 2025}
      {BJJ School}{Bahia, Brazil}
     \resumeItemListStart
        \resumeItem{Taught basic English to kids from low-income households in group sessions.}
        \resumeItem{Created simple materials focused on practical, everyday language.}
        \resumeItem{Kept lessons structured for mixed ages and learning levels.}
        \resumeItem{Coordinated with local staff to keep classes consistent and accessible.}
    \resumeItemListEnd

% -----------Multiple Positions Heading-----------
%    \resumeSubSubheading
%     {Software Engineer I}{Oct 2014 - Sep 2016}
%     \resumeItemListStart
%        \resumeItem{Apache Beam}
%          {Apache Beam is a unified model for defining both batch and streaming data-parallel processing pipelines}
%     \resumeItemListEnd
%    \resumeSubHeadingListEnd
%-------------------------------------------

    \resumeSubheading
      {Website Manager}{Jan. 2022 -- Dec 2024}
      {Jowdah}{Remote, UK}
      \resumeItemListStart
        \resumeItem{Handled SaaS technical issues through Slack and Jira with clear ticket ownership.}
        \resumeItem{Reproduced customer problems and delivered direct fixes or workarounds.}
        \resumeItem{Built and updated email templates with reliable markup and tracking.}
        \resumeItem{Communicated technical updates to customers by email and phone.}
        \resumeItem{Escalated recurring issues to engineering for deeper fixes.}
    \resumeItemListEnd

  \resumeSubHeadingListEnd

%-----------PROGRAMMING SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages}{: HTML, CSS, JavaScript, Email HTML} \\
     \textbf{ESP Experience}{: Klaviyo, Mailchimp, HubSpot} \\
     \textbf{Deliverability Tools}{: Google Postmaster Tools, Litmus} \\
    \textbf{Workflow Tools}{: Jira, Slack, Git, VS Code, Docker, Vim} \\
     \textbf{Operating Systems}{: Windows, macOS, Linux (Debian/Ubuntu/Arch)}
    }}
 \end{itemize}


%-------------------------------------------

%-----------PROJECTS-----------
\section{Projects}
    \resumeSubHeadingListStart
      \resumeProjectHeading
          {\textbf{SudoRootDev} $|$ \emph{YouTube Channel}}{Jan 2022 -- Present}
          \resumeItemListStart
            \resumeItem{Produced concise tutorials on Linux, development workflows, and cloud fundamentals.}
            \resumeItem{Created hands-on examples demonstrating system configuration, tooling, and deployment.}
            \resumeItem{Documented repeatable processes for troubleshooting, automation, and environment setup.}
            \resumeItem{Explained core concepts in a direct, practical format aimed at beginners and intermediates.}
          \resumeItemListEnd
      \resumeProjectHeading
          {\textbf{BeautifulEmails.com} $|$ \emph{Website \& YouTube}}{May 2005 -- May 2010}
          \resumeItemListStart
            \resumeItem{Built and ran BeautifulEmails, reaching \~10K monthly unique visitors.}
            \resumeItem{Published early, widely-viewed tutorials on HTML email development, generating 1.5M+ YouTube views.}
            \resumeItem{Created practical guides that became reference material for new email developers.}
            \resumeItem{Attracted industry attention; the founder of Litmus advertised on the site.}
            \resumeItem{Grew and monetised the platform before selling it to pursue other work.}
        
          \resumeItemListEnd
          \resumeProjectHeading
    {\textbf{HomeLab} $|$ \emph{Networking \& Virtualisation}}{2023 -- Present}
    \resumeItemListStart
        \resumeItem{Managed a home lab with a Ubiquiti router, VLAN segmentation, and basic firewall policy.}
        \resumeItem{Ran Proxmox on a dedicated mini-PC for virtualised test environments and service isolation.}
        \resumeItem{Maintained a NAS for storage, backups, and self-hosted services.}
        \resumeItem{Configured and operated Arch Linux systems, handling installation, user environments, and package management via pacman and the AUR.}
    \resumeItemListEnd

    \resumeSubHeadingListEnd

%

\end{document}
